The genomic impacts of drift and selection for hybrid performance in maize

### 2015-08-26 main.tex
discussion point about BSSS haps is correct

Several key inbreds in the ‘stiff-stalk’ heterotic group, B73, B37 and B14, were derived from the BSSS population \citep{darrah1986, troyer1999background}. 
B37 and B14 were derived from cycle 0, and B73 was derived from a half-sib recurrent selection program also started with the BSSS population. 
We examined these three inbreds at the pericentromeric regions listed in Table \ref{tab:fix} \jri{correct?}, and found that in most cases they carry different haplotypes from those that rose to high frequency in the RRS experiment.  
Near isogenic lines that substitute these centromeric haplotypes from key inbreds could be used to determine if the haplotypes at high frequency in cycle 16 of BSSS provide a phenotypic advantage when crossed with BSCB1.

>>>>

Several key inbreds in the ‘stiff-stalk’ heterotic group, B73, B37 and B14, were derived from the BSSS population \citep{darrah1986, troyer1999background}. 
B37 and B14 were derived from cycle 0, and B73 was derived from a half-sib recurrent selection program also started with the BSSS population. 
We examined these three inbreds at the pericentromeric regions listed in Table \ref{tab:fix}, and found that in most cases they carry different haplotypes from those that rose to high frequency in the RRS experiment.  
Near isogenic lines that substitute these centromeric haplotypes from key inbreds could be used to determine if the haplotypes at high frequency in cycle 16 of BSSS provide a phenotypic advantage when crossed with BSCB1.
